What do incoming university students believe about open science practices in

### 2022-03-29 analysis/Manuscript.Rmd
deleting random words

Our approach to measuring norms and counternorms focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms (see Table \@ref(tab:normcounternormitems)). Although we acknowledge the debatable merits of some of these practices [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.

Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario (see the note accompanying Table \@ref(tab:normcounternormitems)). Participants rated their agreement separately for each norm and counternorm on a 1 (*strongly disagree*) to 5 (*strongly agree*) scale. We used the scenario of a specific researcher rather than referring to psychology researchers in general because it allowed us to make the items more concrete, engaging, and clear.

@@

We also measured participants' normative beliefs about how researchers actually conduct psychological science. We asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to our ten norm–counternorm pairs, with two exceptions (see Table \@ref(tab:normsinpracticeitems)). We excluded the critical thinking norm because it did not refer to externally observable behaviour, and we included another practice out of interest (data availability on request). Participants indicated their estimate on a visual slider from 0% to 100%.

@@

Estimates were recorded using a visual slider from 0% to 100%. 
A second question asked participants whether they had heard of the replication crisis. Those who had heard of the replication crisis were asked two additional open-ended questions: (1) describe the replication crisis, and (2) name the scientific disciplines most affected by the replication crisis.

@@

As preregistered, we calculated the difference in means
between responses to each norm item and its accompanying counternorm (with 
95% confidence intervals). For this analysis, we removed three cases with missing values. 
Table \@ref(tab:differencebetweennormandcounternorm) displays the means and standard deviations for each norm, counternorm, and the difference values. See Table \@ref(tab:corrbetweennormandcounternorm) in the Supplemental Materials for the correlations between norm and counternorm items.

>>>>

To measure norms and counternorms, we focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms (see Table \@ref(tab:normcounternormitems)). Although we acknowledge the debatable merits of some of these practices [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.

Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario (see the note accompanying Table \@ref(tab:normcounternormitems)). Participants rated their agreement separately for each norm and counternorm on a 1 (*strongly disagree*) to 5 (*strongly agree*) scale. We used the scenario of a specific researcher rather than referring to psychology researchers in general because the items were more concrete, engaging, and clear.

@@

We measured participants' normative beliefs about how researchers actually conduct psychological science. We asked, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to our ten norm–counternorm pairs, with two exceptions (see Table \@ref(tab:normsinpracticeitems)). We excluded the critical thinking norm because it did not refer to externally observable behaviour, and we included data availability on request out of interest. Participants provided their estimate on a visual slider from 0% to 100%.

@@

Estimates were recorded using a visual slider from 0% to 100%. 
A second question asked participants whether they had heard of the replication crisis. Those who had heard of the crisis were asked two additional open-ended questions: (1) describe the replication crisis, and (2) name the scientific disciplines most affected by the replication crisis.

@@

As preregistered, we calculated the difference in means
between responses to each norm item and its accompanying counternorm. For this analysis, we removed three cases with missing values. 
Table \@ref(tab:differencebetweennormandcounternorm) displays the means and standard deviations for each norm, counternorm, and the difference values. See Table \@ref(tab:corrbetweennormandcounternorm) in the Supplemental Materials for the correlations between norm and counternorm items.
